Machine Learning Model for Agricultural Data Applications

### 2021-03-05 paper.tex
Rename machineLearningModelsForAgriculture.tex to paper.tex
Template

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
	\caption{Machine Learning Workflow.}
	\label{fig:workflow}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
	\caption{Extract Transform Load.}
	\label{fig:ETL}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
	\caption{Raw Data Area.}
	\label{fig:Areaa_Head1}
\end{figure}

@@

A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
\begin{figure}
	\centering
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{areaHectares.png}
		\caption{Area}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{gpv.png}
		\caption{G.P.V}
		\label{fig:sub2}
	\end{subfigure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{yield.png}
		\caption{Yield}
		\label{fig:sub3}
	\end{subfigure}
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
		\caption{Quantity}
		\label{fig:sub4}
	\end{subfigure}

>>>>

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/workflow.png}
	\caption{Machine Learning Workflow.}
	\label{fig:workflow}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/etl.jpg}
	\caption{Extract Transform Load.}
	\label{fig:ETL}
\end{figure}

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Area_Head.png}
	\caption{Raw Data Area.}
	\label{fig:Areaa_Head1}
\end{figure}

@@

A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
\begin{figure}
	\centering
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/areaHectares.png}
		\caption{Area}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/gpv.png}
		\caption{G.P.V}
		\label{fig:sub2}
	\end{subfigure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/yield.png}
		\caption{Yield}
		\label{fig:sub3}
	\end{subfigure}
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/quantityTonnes.png}
		\caption{Quantity}
		\label{fig:sub4}
	\end{subfigure}
